Analytics Without Tuning Considered Harmful?

### 2015-08-12 tuningpredictor.tex

\subsection{RQ2:  Does Tuning Change a Learner's Ranking ?}\label{sect:rank}
Researchers often use performance criteria to assert that one learner is better than another~\cite{lessmann2008benchmarking,me07b}. In\cite{me07b}, naive Bayes does better than C4.5 in terms of pd and balance over NASA MDP data sets. In \cite{lessmann2008benchmarking}, Random Forest is considered to be statistically better than CART in terms of the AUC ranking. Such conclusions are not reliable since they can change when we elect to tune for different goals.

@@

\begin{figure}[!t]
\begin{center}
\includegraphics[width=1.5in]{LR_untuned.eps}\includegraphics[width=1.5in]{LR_tuned.eps}
 \end{center}
\caption{Comparison between tuned and naive SVM learners with rbf and sigmoid kernels over the goal of F. }\label{fig:svm}
 \end{figure}

@@

To justify that {\em np=10} is enough, we did another tuning study, 
where all the settings were the same as before but we set{\em np= 90, 50} and {\em np = 60} for WHERE, CART and Random Forests as recommended by Storn. The tuning performance of learners was evaluated
by precision and F. To compare performance of each learner with different np's, we plot the delta in the performance as \fig{deltas}. As shown in \fig{deltas_np}, in terms of precision, the recommended {\em np} will improve the performance of WHERE, CART and Random Forests in 2, 5, and 4 data sets. However, in 6, 4, and 4 data sets, those numbers  will degrade the performance compared with {\em np = 10}. For F as the tuning goal, we can observe the similar pattern.

>>>>

\subsection{RQ2:  Does Tuning Change a Learner's Ranking Regarding Different Goals?}\label{sect:rank}
Researchers often use performance criteria to assert that one learner is better than another~\cite{lessmann2008benchmarking,me07b}. In\cite{me07b}, naive Bayes does better than C4.5 in terms of pd and balance over NASA MDP data sets. In \cite{lessmann2008benchmarking}, Random Forest is considered to be statistically better than CART in terms of the AUC ranking. Such conclusions are not reliable since they can change when we elect to tune for different goals.

@@

@@

To justify that {\em np=10} is enough, we did another tuning study, 
where all the settings were the same as before but we set{\em np= 90, 50} and {\em np = 60} for WHERE, CART and Random Forests as recommended by Storn. The tuning performance of learners was evaluated
by precision and F. To compare performance of each learner with different np's, we plot the delta in the performance as \fig{deltas}. As shown in \fig{deltas_np}, in terms of precision, the recommended {\em np} will improve the performance of WHERE, CART and Random Forests in 2, 5, and 4 data sets. However, in 6, 4, and 4 data sets, those numbers  will deteriorate the performance compared with {\em np = 10}. For F as the tuning goal, we can observe the similar pattern.
